ForOpenCL: Transformations Exploiting Array Syntax in Fortran for Accelerator Programming

### 2011-11-27 papers/IJCSE/foropencl.tex
edits

\documentclass{acm_proc_article-sp}

@@

@@

\numberofauthors{6}

\author{
% 1st. author
\alignauthor
Matthew J. Sottile\\
       \affaddr{Galois, Inc.}\\
%       \affaddr{421 SW 6th Ave. Suite 300}\\
       \affaddr{Portland, OR 97204}\\
       \email{mjsottile@computer.org}
% 2nd. author
\alignauthor
Craig E Rasmussen\\
       \affaddr{Los Alamos National Laboratory}\\
%       \affaddr{CCS-7, MS B287}\\
       \affaddr{Los Alamos, NM 87545}\\
       \email{crasmussen@lanl.gov}
% 3rd. author
\alignauthor
Wayne N. Weseloh\\
       \affaddr{Los Alamos National Laboratory}\\
       %\affaddr{XTD-1, MS T082}\\
       %\affaddr{Los Alamos, NM 87545}\\
       \email{weseloh@lanl.gov}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Robert W. Robey\\
       \affaddr{Los Alamos National Laboratory}\\
       %\affaddr{XCP-2, MS T086}\\
       %\affaddr{Los Alamos, NM 87545}\\
       \email{brobey@lanl.gov}
% 5th. author
\alignauthor
Daniel Quinlan\\
       \affaddr{Lawrence Livermore National Laboratory}\\
       \email{dquinlan@llnl.gov}
% 6th. author
\alignauthor
Jeffrey Overbey\\
       \affaddr{University of Illinois at Urbanna-Champaign}\\
       \email{overbey2@illinois.edu}
}

@@

\balancecolumns
\end{document}

>>>>

\documentclass{doublecol-new}

@@

\LRH{M. Sottile et~al.}

\RRH{ForOpenCL: Transformations Exploiting Array Syntax in Fortran for Accelerator Programming}

@@

% 1st. author
\authorA{Matthew J. Sottile}
\affA{Galois, Inc.\\
 Portland, OR 97204\\
 E-mail: mjsottile@computer.org}

% 2nd. author
\authorB{Craig E Rasmussen}
\affB{Los Alamos National Laboratory\\
 Los Alamos, NM 87545\\
 E-mail: crasmussen@lanl.gov}

% 3rd. author
\authorC{Wayne N. Weseloh}
\affC{Los Alamos National Laboratory\\
 Los Alamos, NM 87545\\
 E-mail: weseloh@lanl.gov}

% 4th. author
\authorD{Robert W. Robey}
\affD{Los Alamos National Laboratory\\
 Los Alamos, NM 87545\\
 E-mail: brobey@lanl.gov}

% 5th. author
\authorE{Daniel Quinlan}
\affE{Lawrence Livermore National Laboratory\\
 Livermore, CA 94550\\
 E-Mail: dquinlan@llnl.gov}

% 6th. author
\authorF{Jeffrey Overbey}
\affF{University of Illinois at Urbanna-Champaign\\
 Champaign, IL 61820\\
 E-mail: overbey2@illinois.edu}

@@

\end{document}

### 2011-11-27 papers/IJCSE/programming-model.tex
edits

An interesting line of language research that grew out of HPF was that
associated with the ZPL language at the University of
Washington~\cite{chamberlain04zpl} and Chapel, an HPCS language developed by
Cray~\cite{chamberlain_chapel}.  In ZPL, programmers adopt a similar global view
of computation over arrays, but define their computations based on regions,
which provide a local view of the set of indices that participate in the update
of each element of an array.  A similar line of research in the functional
language community has investigated array abstractions for expressing
whole-array operations in the Haskell language in the REPA (regular, shape-polymorphic,
parallel array) library~\cite{keller10repa}.

>>>>

An interesting line of language research that grew out of HPF was that
associated with the ZPL language at the University of
Washington~\cite{chamberlain04zpl} and Chapel, an HPCS language developed by
Cray~\cite{chamberlainchapel}.  In ZPL, programmers adopt a similar global view
of computation over arrays, but define their computations based on regions,
which provide a local view of the set of indices that participate in the update
of each element of an array.  A similar line of research in the functional
language community has investigated array abstractions for expressing
whole-array operations in the Haskell language in the REPA (regular, shape-polymorphic,
parallel array) library~\cite{keller10repa}.
